Ms 1

### 2017-06-16 ms1/ms1_display.Rmd
updated display

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace, str_detect)
import::from(forcats, as_factor)

@@

```{r}
read_tsv('tables/tbl_totals.tsv') %>%
  pctize('n_bene') %>%
  select(year, n_bene, mean_age, mean_n_cc,
         pct_female, pct_white, pct_dual,
         pct_region_south, pct_region_midwest, pct_region_northeast, pct_region_west) %>%
  mutate_at(vars(starts_with('pct_')), function(x) round(x, digits=1)) %>%
  mutate(n_bene=prettyNum(n_bene, big.mark=','),
         mean_age=round(mean_age, digits=1),
         mean_n_cc=round(mean_n_cc, digits=2)) %>%
  gather('var', 'val', -year) %>% spread(year, val) %>% # transpose
  kable
```

@@

```{r}
read_tsv('tables/tbl_cohort_totals.tsv') %>%
  pctize('n_bene') %>%
  select(year, n_bene, mean_age, mean_n_cc,
         pct_female, pct_white, pct_dual,
         pct_region_south, pct_region_midwest, pct_region_northeast, pct_region_west) %>%
  mutate_at(vars(starts_with('pct_')), function(x) round(x, digits=1)) %>%
  mutate(n_bene=prettyNum(n_bene, big.mark=','),
         mean_age=round(mean_age, digits=1),
         mean_n_cc=round(mean_n_cc, digits=2)) %>%
  gather('var', 'val', -year) %>% spread(year, val) %>% # transpose
  kable
```

@@

```{r}
dat = read_tsv('tables/tbl_claims_by_abx.tsv')
cohort_dat = read_tsv('tables/tbl_cohort_claims_by_abx.tsv')

top_abx = dat %>%
  group_by(antibiotic) %>%
  summarize(cpkp=mean(cpkp)) %>%
  arrange(desc(cpkp)) %$%
  head(antibiotic, 10)

@@

  df %>%
    select(antibiotic, year, cpkp) %>%
    filter(antibiotic %in% top_abx) %>%
    bind_rows(totals) %>%
    mutate(antibiotic=factor(antibiotic, levels=c('all', top_abx)))
}

@@

```{r}
all_dat %>%
  arrange(group, antibiotic, year) %>%
  group_by(group, antibiotic) %>%
  summarize(p.value=trend_p(cpkp)) %>%
  ungroup() %>%
  mutate(adj.p.value=p.adjust(p.value, method='BH')) %>%
  select(antibiotic, group, adj.p.value) %>%
  spread(group, adj.p.value) %>%
  mutate(sig=if_else(all < 0.05 | cohort < 0.05, '*', '')) %>%
  kable
```

This shows a summary of the above data, using percent changes from 2011 to 2014:

```{r}
all_dat %>%
  arrange(year) %>%
  group_by(group, antibiotic) %>%
  summarize(mean_cpkp=mean(cpkp),
            pct_change=(tail(cpkp, 1)/head(cpkp, 1) - 1)*100) %>%
  ungroup() %>%
  filter(antibiotic %in% top_abx) %>%
  { levels = filter(., group=='cohort') %>% arrange(pct_change) %$% antibiotic;
    mutate(., antibiotic=factor(.$antibiotic, levels=levels)) } %>%
  ggplot(aes(x=antibiotic, y=pct_change, color=group)) +
  geom_point() +
  coord_flip()
```

@@

```{r claims_by_age}
read_tsv('tables/tbl_claims_by_age.tsv') %>%
  mutate(cpkp=round(cpkp)) %>%
  select(year, age_group, cpkp) %>%
  spread(year, cpkp) %>%
  kable
```

@@

```{r}
read_tsv('tables/tbl_claims_by_sex.tsv') %>%
  select(sex, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-sex), round) %>%
  kable
```

@@

```{r}
read_tsv('tables/tbl_claims_by_region.tsv') %>%
  select(region, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-region), round) %>%
  kable
```

@@

```{r}
read_tsv('tables/tbl_claims_by_race.tsv') %>%
  select(race, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-race), round) %>%
  kable
```

@@

"Adjusted" means the `year` coefficient in `y ~ year + age*n_cc + is_female + is_dual + is_white + region`.

@@

```{r}
read_tsv('tables/tbl_cohort_model_azithro.tsv') %>% kable
```

@@

```{r}
read_tsv('tables/tbl_cohort_model_levo.tsv') %>% kable
```

@@

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace, str_detect)
import::from(forcats, as_factor)

@@

@@

```{r}
totals_dat = read_tsv('tables/tbl_cohort_totals.tsv') %>%
  pctize('n_bene') %>%
  select(year, n_bene, mean_age, sd_age, mean_n_cc, sd_n_cc,
         pct_female, pct_white, pct_dual,
         pct_region_south, pct_region_midwest, pct_region_northeast, pct_region_west)

totals_dat %>%
  mutate_at(vars(starts_with('pct_')), function(x) round(x, digits=1)) %>%
  mutate(n_bene=prettyNum(n_bene, big.mark=','),
         mean_age=round(mean_age, digits=1)) %>%
  mutate_at(vars(mean_n_cc, sd_age, sd_n_cc),
            function(x) round(x, digits=2)) %>% 
  gather('var', 'val', -year) %>% spread(year, val) %>% # transpose
  kable
```

```{r}
linear_trend_p = function(x) tidy(t.test(diff(x)))$p.value

totals_dat %>%
  gather('var', 'val', -year) %>%
  arrange(var, year, val) %>%
  group_by(var) %>%
  summarize(p=linear_trend_p(val)) %>%
  mutate(adj.p=p.adjust(p, method='BH'),
         sig=if_else(adj.p<0.05, '*', '')) %>%
  kable
```

@@

```{r}
cohort_dat = read_tsv('tables/tbl_cohort_claims_by_abx.tsv')

top_abx = cohort_dat %>%
  group_by(antibiotic) %>%
  summarize(cpkp=mean(cpkp)) %>%
  arrange(desc(cpkp)) %$%
  head(antibiotic, 10)

@@

  df %>%
    select(antibiotic, year, cpkp) %>%
    filter(antibiotic %in% top_abx) %>%
    bind_rows(totals) %>%
    mutate(antibiotic=factor(antibiotic, levels=c('all', top_abx)))
}
```

```{r}
cohort_dat %>%
  top_abx_f() %>%
  ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~ antibiotic, ncol=3, scales='free_y') +
  geom_point() + geom_line() +
  theme_minimal() +
  ggtitle('Unadjusted consumption, in cohort')

cohort_dat %>%
  top_abx_f() %>%
  filter(year %in% c(2011, 2014)) %>%
  spread(year, cpkp) %>%
  mutate(pct_change=(`2014`-`2011`)/`2011`*100) %>%
  kable
```

@@

```{r}
cohort_dat %>%
  top_abx_f() %>%
  arrange(antibiotic, year) %>%
  group_by(antibiotic) %>%
  summarize(p.value=trend_p(cpkp)) %>%
  ungroup() %>%
  mutate(adj.p.value=p.adjust(p.value, method='BH')) %>%
  select(antibiotic, adj.p.value) %>%
  mutate(sig=if_else(adj.p.value < 0.05, '*', '')) %>%
  kable
```

@@

```{r claims_by_age}
read_tsv('tables/tbl_cohort_claims_by_age.tsv') %>%
  mutate(cpkp=round(cpkp)) %>%
  select(year, age_group, cpkp) %>%
  spread(year, cpkp) %>%
  kable
```

@@

```{r}
read_tsv('tables/tbl_cohort_claims_by_sex.tsv') %>%
  select(sex, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-sex), round) %>%
  kable
```

@@

```{r}
read_tsv('tables/tbl_cohort_claims_by_region.tsv') %>%
  select(region, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-region), round) %>%
  kable
```

@@

```{r}
read_tsv('tables/tbl_cohort_claims_by_race.tsv') %>%
  select(race, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-race), round) %>%
  kable
```

@@

"Adjusted" means the `year` coefficient in `y ~ year + age + n_cc + is_female + is_dual + is_white + region`.

@@

```{r}
read_tsv('tables/tbl_cohort_model_azithro.tsv') %>%
  mutate(cpkp=estimate*1000) %>%
  filter(term != '(Intercept)') %>%
  select(term, cpkp, p.value) %>%
  kable
```

@@

```{r}
read_tsv('tables/tbl_cohort_model_levo.tsv') %>%
  mutate(cpkp=estimate*1000) %>%
  filter(term != '(Intercept)') %>%
  select(term, cpkp, p.value) %>%
  kable
```

@@

# Supplemental results

## Summary of data for the entire group

```{r}
read_tsv('tables/tbl_totals.tsv') %>%
  pctize('n_bene') %>%
  select(year, n_bene, mean_age, sem_age, mean_n_cc, sem_n_cc,
         pct_female, pct_white, pct_dual,
         pct_region_south, pct_region_midwest, pct_region_northeast, pct_region_west) %>%
  mutate_at(vars(starts_with('pct_')), function(x) round(x, digits=1)) %>%
  mutate(n_bene=prettyNum(n_bene, big.mark=','),
         mean_age=round(mean_age, digits=1),
         mean_n_cc=round(mean_n_cc, digits=2)) %>%
  gather('var', 'val', -year) %>% spread(year, val) %>% # transpose
  kable
```

## Consumption trends in both groups

```{r}
dat = read_tsv('tables/tbl_claims_by_abx.tsv')
